---
title: "Principal-protected Floating-income Strucured product - CSI Index | by Zhizhong Peng"
output: html_document
---

# Designed two structured product: Product 1 and Product 2
- Designed/Customized two principal protected CSI Index floating income structured products (product 1 and 2), and use the actual distirbution to do Monte Carlo Simulation, then esimate the two products' distributions of the Total return at maturity. So financial advisors and clients can see what the profitability will be like.
- Data Source for CSI Daily Price: Refinitiv, from 2005-01-11 to 2021-12-30. Attached EXCEL file.

## Principal-protected Floating-income Strucured product - CSI Index (Product 1 and Product 2)
 
### Product 1: 
- The product maturity is 180 natural days (N = 128) 
	- Strike price 1: (price_{T0}) * 95%
	- Strike price 2: (price_{T0}) * 105%
- Target Index: .CSI300 (China Shanghai Shenzhen 300 Index)
- Calculation Rule of income at maturity: 
	- Fixed rate of income: 0.1%
	- Floating rate of income: (0% * M1 + 4.4% * M2 + 0% * M3) / N
		- M1: From T0 to Tn, the number of the trading day as the CSI300's price-closed lower or equal to Strike price 1
		- M2: From T0 to Tn, the number of the trading day as the CSI300's price-closed higher the Strike price 1 and lower the Strike price 2
		- M3: From T0 to Tn, the number of the trading day as the CSI300's price-closed higher the  Strike price 1
		- N: From T0 to Tn, the number of trading day
- Total return at matrity = Fixed rate of income + Floating rate of income
    
### Product 2: 
- The product maturity is 180 natural days (N = 128) 
	- Strike price 1: (price_{T0}) * 95%
	- Strike price 2: (price_{T0}) * 98%
	- Strike price 3: (price_{T0}) * 102%
	- Strike price 4: (price_{T0}) * 105%
- Target Index: .CSI300 (China Shanghai Shenzhen 300 Index)
- Calculation Rule of income at maturity: 
	- Fixed rate of income: 0.1%
	- Floating rate of income: (0% * M1 + 3% * M2 + 5.9% * M3 + 3% * M4 + 0% * M5) / N
		- M1: From T0 to Tn, the number of the trading day as the CSI300's price-closed lower or equal to Strike price 1
		- M2: From T0 to Tn, the number of the trading day as the CSI300's price-closed higher the  Strike price 1 and lower the Strike price 2
		- M2: From T0 to Tn, the number of the trading day as the CSI300's price-closed higher the  Strike price 2 and lower the Strike price 3
		- M3: From T0 to Tn, the number of the trading day as the CSI300's price-closed higher the  Strike price 4
		- N: From T0 to Tn, the number of trading day
- Total return at matrity = Fixed rate of income + Floating rate of income

```{r}
library(xts) # to manipulate time series of stock data
library(rtsdata) # export xts to excel
Tol18rainbow = c("#771155","#AA4488","#CC99BB","#114477","#4477AA", 
                 "#77AADD","#117777","#44AAAA","#77CCCC","#777711", 
                 "#AAAA44","#DDDD77","#774411","#AA7744","#DDAA77", 
                 "#771122","#AA4455","#DD7788") 

```


```{r, echo=FALSE, message=FALSE, warning=FALSE}

library(readxl)
CSI300 <- readxl::read_excel("D:\\Desktop\\GF_Securities\\Price History_20211230_0914.xlsx", 
                             #index = CSI300[,1], 
                             col_type=c("date", "numeric","numeric","numeric",
                                        "numeric","numeric","numeric","numeric",
                                        "numeric","numeric","numeric","numeric",
                                        "numeric","numeric","numeric","numeric"))[c(27:4160),c(1:10)]
colnames(CSI300) <- readxl::read_excel("D:\\Desktop\\GF_Securities\\Price History_20211230_0914.xlsx")[c(26),c(1:10)]
head(CSI300)
str(CSI300)
tail(CSI300)
```



```{r fig.width=12, fig.height=6, message=FALSE, warning=FALSE}
library(timetk)
CSI300 <- timetk::tk_xts(CSI300, date_col = CSI300[,1])
head(CSI300)
tail(CSI300)


data <- cbind(CSI300[,1], 
              rollapplyr(CSI300[,3], width = 20, FUN = sd, na.rm = TRUE))


par(fig=c(0,1,0,1), new=TRUE)
plot.xts(data[,1],  col = "gray", mar = c(5, 2, 2, 5),
         main="CSI 300 Price Chart (Daily Close)", type = "h", auto.grid = FALSE)
par(fig=c(0,1,0,1), new=TRUE)
plot.xts(data[,2], col = 2, mar = c(5, 2, 2, 5),
         main="CSI 300 Price Chart (30 Day rolling StdDev)", auto.grid = FALSE)






```

```{r fig.width=12, fig.height=6, message=FALSE, warning=FALSE}
library(timetk)
CSI300 <- timetk::tk_xts(CSI300, date_col = CSI300[,1])
head(CSI300)
tail(CSI300)

#####################################################
data <- CSI300[,3]
getmode <- function(v) {
   uniqv <- unique(v)
   uniqv[which.max(tabulate(match(v, uniqv)))]
}
hist(data, breaks = 512, 
     probability=TRUE, border=FALSE, xaxt="n", ylab = "Density (%)",
     main = "",xlab="",
     sub = paste0("Mean=",round(mean(data)*100,3),"%",
                  ", StdDev=",round(sd(data*100),3),"%",
                  ", Median=",round(median(data*100),3),"%",
                  ", Mode=",round(getmode(data*100),3),"%",
                  ", Skew=",round(e1071::skewness(data),3),
                  ", Kurt=",round(e1071::kurtosis(data),3),"+3",
                  ", \nMax=",round(max(data)*100,3),"%",
                  ", Min=",round(min(data)*100,3),"%",
                  ", PCTL95%=",round(quantile(data, 0.95)*100,3),"%",
                  ", PCTL5%=",round(quantile(data, 0.05)*100,3),"%")) # Histogram
title(main = "Probability Density Plot of CSI 300 (Daily Reward)", xlab="Daily Reward", adj = 0)
axis(side=1, at=pretty(x=data,n=22), 
     lab=paste0(pretty(data,n=22) * 100,"%"), las=1) # x tick

(kernels <- eval(formals(density.default)$kernel))
bw <- bw.SJ(as.vector(data)) ## sensible automatic choice
for(i in 1:length(kernels)) {
   lines(density(as.vector(data), bw = bw, kernel = kernels[i]), col = Tol18rainbow[i])}
lines(density(data, bw=bw, kernel="gaussian"),col="blue",pch=22, lwd=3) # Actual Density (KDE)

grid(nx = NA, ny = NULL, lty = 2, col = "gray", lwd = 1)
grid(nx = NULL, ny = NA, lty = 1, col = "gray", lwd = 1)

x <- seq(min(data), max(data), length = length(data))
f <- dnorm(x, mean = mean(data), sd = sd(data))
lines(x, f, col = "red", lwd = 3) # Normal

legend("topright", c("Actual Histogram", paste0("Actual Density (Gaussian KDE), \nBandwidth=",bw), 
                     paste0("Normal(","Mean=",round(mean(data)*100,3),"%",
                            ", StdDev=",round(sd(data),3),"%)")), 
       box.lty = 3, lty = 1, bty="n", col = c("black", "blue", "red"), lwd = c(1, 3, 3))
abline(v = getmode(data), col = "cyan",lty = 3)
abline(v = quantile(data, 0.05), col = "Black",lty = 3)
abline(v = quantile(data, 0.95), col = "Black",lty = 3)
abline(v = median(data), col = "Green",lty = 3)
abline(v = mean(data), col = "Purple",lty = 3)
abline(v = quantile(data, c(0.25, 0.75)), col = "Orange",lty = 3)
boxplot(data, add=TRUE,horizontal=TRUE,at=-1.0,col = "lightgray",
        border="black",boxwex=2.5,outline=TRUE,xlab="n", ylab="n",axes=FALSE)

#####################################################



CSI300stdev20 <- na.omit(rollapplyr(CSI300[,3], width = 20, FUN = sd, na.rm = TRUE))
getmode <- function(v) {
   uniqv <- unique(v)
   uniqv[which.max(tabulate(match(v, uniqv)))]
}


hist(CSI300stdev20, breaks = 512, xaxt="n", freq=FALSE, border=FALSE, ylab = "Density (%)",
     main = "", xlab="",right=TRUE, 
     sub = paste0("Mean=",round(mean(CSI300stdev20)*100,3),"%",
                  ", StdDev=",round(sd(CSI300stdev20*100),3),"%",
                  ", Median=",round(median(CSI300stdev20*100),3),"%",
                  ", Mode=",round(getmode(CSI300stdev20*100),3),"%",
                  ", Skew=",round(e1071::skewness(CSI300stdev20),3),
                  ", Kurt=",round(e1071::kurtosis(CSI300stdev20),3),"+3",
                  ", \nMax=",round(max(CSI300stdev20)*100,3),"%",
                  ", Min=",round(min(CSI300stdev20)*100,3),"%",
                  ", PCTL95%=",round(quantile(CSI300stdev20, 0.95)*100,3),"%",
                  ", PCTL5%=",round(quantile(CSI300stdev20, 0.05)*100,3),"%")) # Histogram)
title(main = "Probability Density Plot of CSI 300 (30 day Hist StdDev)", xlab="30 Day rolling StdDev", adj = 0)
axis(side=1, at=pretty(x=CSI300stdev20,n=20), 
     lab=paste0(pretty(CSI300stdev20,n=20) * 100,"%"), las=2) # x tick

(kernels <- eval(formals(density.default)$kernel))
bw <- bw.SJ(as.vector(CSI300stdev20)) ## sensible automatic choice
for(i in 1:length(kernels)) {
   lines(density(as.vector(CSI300stdev20), bw = bw, kernel = kernels[i]), col = Tol18rainbow[i])}
lines(density(CSI300stdev20, bw=bw, kernel="gaussian"),col="blue",pch=22, lwd=3) # Actual Density (KDE)
grid(nx = NA, ny = NULL, lty = 2, col = "gray", lwd = 1)
grid(nx = NULL, ny = NA, lty = 1, col = "gray", lwd = 1)
legend("topright", c("Actual Histogram", paste0("Actual Density (Gaussian KDE), \nBandwidth=",bw)), 
       box.lty = 3, lty = 1 ,bty="n", col = c("black", "blue"), lwd = c(1, 3))
abline(v = getmode(CSI300stdev20), col = "cyan",lty = 3)
abline(v = quantile(CSI300stdev20, 0.05), col = "Black",lty = 3)
abline(v = quantile(CSI300stdev20, 0.95), col = "Black",lty = 3)
abline(v = median(CSI300stdev20), col = "Green",lty = 3)
abline(v = mean(CSI300stdev20), col = "Purple",lty = 3)
abline(v = quantile(CSI300stdev20, c(0.25, 0.75)), col = "Orange",lty = 3)
boxplot(CSI300stdev20, add=TRUE,horizontal=TRUE,at=-2,col = "lightgray",
        border="black",boxwex=5.0,outline=TRUE,xlab="n", ylab="n",axes=FALSE)


#####################################################


# QQ plot
#qqnorm(data,breaks = 100, main="QQ Plot of CSI 300", pch=19)
#qqline(data)
#grid(nx = NA, ny = NULL, lty = 2, col = "gray", lwd = 1)


#####################################################
## Performs the Shapiro-Wilk test of normality.
# Hypothesis test for a test of normality
# Null hypothesis: The data is normally distributed. If p> 0.05, normality can be assumed.
shapiro.test(as.vector(data))
# For the CSI 300 Daliy Close data, p < 2.2e-16 suggesting strong evidence of 
# non-normality and non-parametric test should be used 
density(data)
str(density(data))

# Find the best and worest day
find_the_point <- min(data)
round(CSI300[min(which.min(abs(data - find_the_point))),3],3)
find_the_point <- max(data)
round(CSI300[min(which.min(abs(data - find_the_point))),3],3)


#####################################################
#(kernels <- eval(formals(density.default)$kernel))
#bw <- bw.SJ(as.vector(data)) ## sensible automatic choice
#plot(density(data, bw=bw)$x, density(data, bw=bw)$y, col="Blue")

#bw <- bw.SJ(as.vector(CSI300stdev20)) ## sensible automatic choice
#points(density(CSI300stdev20, bw=bw)$x, density(CSI300stdev20, bw=bw)$y, col="Red")

#####################################################
#hist(density(data, bw=bw)$x, breaks = 100, )
```


```{r fig.width=12, fig.height=6, message=FALSE, warning=FALSE}
#####################################################
#####################################################
#####################################################
# Create data.
data <- CSI300[,3]
x <- data
# `dx` is the density function, used later for plotting. 
# If we able to find the perfect distirbution
# dx <- function(x) (dnorm(x) + dnorm(x, 4, 1/4) + dnorm(x, 8, 1/4))/3
# Compute a kernel density estimate.
# It returns a kernel width in $bw as well as $x and $y vectors for plotting.
(kernels <- eval(formals(density.default)$kernel))
bw <- bw.SJ(as.vector(x)) ## sensible automatic choice
#plot(density(x, bw=bw)$x, density(x, bw=bw)$y, col="Blue")
z <- density(x, bw=bw, kernel="gaussian")
##### Sample from the KDE.
# Define a function to sample from the density.
# This one implements only a Gaussian kernel.
rdens <- function(n, density=z, data=x, kernel="gaussian") {
  width <- z$bw                              # Kernel width
  rkernel <- function(n) rnorm(n, sd=width)  # Kernel sampler
  sample(x, n, replace=TRUE) + rkernel(n)    # Here's the entire algorithm
}
# simulation (sampling)
n <- 1000000
#set.seed(888)
system.time(y <- rdens(n, z, x)) # Millions per second
# Plot the sample.
h.density <- hist(y, breaks=512, plot=TRUE)


#####################################################
data <- y
getmode <- function(v) {
   uniqv <- unique(v)
   uniqv[which.max(tabulate(match(v, uniqv)))]
}
hist(data, breaks = 512, 
     probability=TRUE, border=FALSE, xaxt="n", ylab = "Density (%)",
     main = "",xlab="",
     sub = paste0("Mean=",round(mean(data)*100,3),"%",
                  ", StdDev=",round(sd(data*100),3),"%",
                  ", Median=",round(median(data*100),3),"%",
                  ", Mode=",round(getmode(data*100),3),"%",
                  ", Skew=",round(e1071::skewness(data),3),
                  ", Kurt=",round(e1071::kurtosis(data),3),"+3",
                  ", \nMax=",round(max(data)*100,3),"%",
                  ", Min=",round(min(data)*100,3),"%",
                  ", PCTL95%=",round(quantile(data, 0.95)*100,3),"%",
                  ", PCTL5%=",round(quantile(data, 0.05)*100,3),"%")) # Histogram
title(main = paste0("Simulated Probability Density Plot of CSI 300 (Daily Reward), n=",n), xlab="Daily Reward", adj = 0)
axis(side=1, at=pretty(x=data,n=22), 
     lab=paste0(pretty(data,n=22) * 100,"%"), las=1) # x tick


for(i in 1:length(kernels)) { lines(density(as.vector(data), bw = bw, kernel = kernels[i]), col = Tol18rainbow[i]) }
lines(density(data, bw=bw, kernel="gaussian"),col="blue",pch=22, lwd=3) # Actual Density (KDE)

grid(nx = NA, ny = NULL, lty = 2, col = "gray", lwd = 1)
grid(nx = NULL, ny = NA, lty = 1, col = "gray", lwd = 1)

x <- seq(min(data), max(data), length = length(data))
f <- dnorm(x, mean = mean(data), sd = sd(data))
lines(x, f, col = "red", lwd = 3) # Normal

legend("topright", c("Actual Histogram", paste0("Actual Density (Gaussian KDE), \nBandwidth=",bw), 
                     paste0("Normal(","Mean=",round(mean(data)*100,3),"%",
                            ", StdDev=",round(sd(data),3),"%)")), 
       box.lty = 3, lty = 1 ,bty="n", col = c("black", "blue", "red"), lwd = c(1, 3, 3))
abline(v = getmode(data), col = "cyan",lty = 3)
abline(v = quantile(data, 0.025), col = "Black",lty = 3)
abline(v = quantile(data, 0.975), col = "Black",lty = 3)
abline(v = median(data), col = "Green",lty = 3)
abline(v = mean(data), col = "Purple",lty = 3)
abline(v = quantile(data, c(0.25, 0.75)), col = "Orange",lty = 3)
boxplot(data, add=TRUE,horizontal=TRUE,at=-0.95,col = "lightgray",
        border="black",boxwex=2.5,outline=TRUE,xlab="n", ylab="n",axes=FALSE)

#####################################################

```

```{r fig.width=12, fig.height=6, message=FALSE, warning=FALSE}
#####################################################
#####################################################
#####################################################


# Create data.
data <- CSI300[,3]
x <- as.vector(data)
# `dx` is the density function, used later for plotting. 
# If we able to find the perfect distirbution
# dx <- function(x) (dnorm(x) + dnorm(x, 4, 1/4) + dnorm(x, 8, 1/4))/3
# Compute a kernel density estimate.
# It returns a kernel width in $bw as well as $x and $y vectors for plotting.
(kernels <- eval(formals(density.default)$kernel))
bw <- bw.SJ(as.vector(x)) ## sensible automatic choice
#plot(density(x, bw=bw)$x, density(x, bw=bw)$y, col="Blue")
z <- density(x, bw=bw, kernel="gaussian")

##### Sample from the KDE.
# Define a function to sample from the density.
# This one implements only a Gaussian kernel.
rdens <- function(n, density=z, data=x, kernel="gaussian") {
  width <- z$bw                              # Kernel width
  rkernel <- function(n) rnorm(n, sd=width)  # Kernel sampler
  sample(x, n, replace=TRUE) + rkernel(n)    # Here's the entire algorithm
}
# simulation (sampling)
n <- 180
m <- 10000
df <- matrix(ncol = n, nrow = m)

for (i in 1:m) {
  #set.seed(888)
  y <- rdens(n, z, x) # Millions per second
  # Plot the sample.
  #h.density <- hist(y, breaks=512, plot=TRUE)
  df[i,] <- t(y)
}


df <- data.frame(t(df))
for (i in 1:nrow(df)) {
  rownames(df)[[i]] <- (as.Date("2021-12-31", origin = "1899-12-30") + i+25568)
}
rownames(df) <- as.Date(as.double(rownames(df)), origin = "1899-12-30")
#head(df)
#tail(df)

df <- df[lubridate::wday(rownames(df)) < 6,]

df1 <- df
df1 <- as.xts(df1)
cum_return <- cumprod(1 + df1)

library(scales)


pctl50 <- cum_return[,1]
pctl95 <- cum_return[,1]
pctl05 <- cum_return[,1]
excu_95 <- cum_return[,1]
excu_98 <- cum_return[,1]
excu_102 <- cum_return[,1]
excu_105 <- cum_return[,1]

for (i in 1:nrow(cum_return[,1:ncol(cum_return)])) {
  pctl95[i] <- quantile(cum_return[i,1:ncol(cum_return)], 0.95)
  pctl05[i] <- quantile(cum_return[i,1:ncol(cum_return)], 0.05)
  pctl50[i] <- quantile(cum_return[i,1:ncol(cum_return)], 0.50)
  # product
  excu_95[i] <- 1 * 0.95
  excu_98[i] <- 1 * 0.98
  excu_102[i] <- 1 * 1.02
  excu_105[i] <- 1 * 1.05
}


ybounds <- function(y){  # y is the response variable in the dataframe
  a = min(y) 
  b = max(y) 
    return( c(a, b) )
}

ybounds(pctl95)

plot_only_show <- if (ncol(cum_return) >= 5) { 5 } else {ncol(cum_return)} 
{ plot.xts(cum_return[,1:plot_only_show], 
           ylim = ybounds(cbind(cum_return[,1:plot_only_show],pctl95,pctl05,pctl50,excu_95,excu_98,excu_102,excu_105)),
           col = scales::alpha(c(Tol18rainbow), 0.8), # or Tol18rainbow
           type="o", pch=19,
           main = paste0("CSI300 Random Walk ", nrow(cum_return)," trading days , simulated ", m," times, only show first ", plot_only_show), 
           xaxt='n',screens = 1)
  lines(cbind(pctl95,pctl05), col = "blue", on=1, lwd = 2)
  lines(pctl50, col = "black", on=1, lwd = 2)
  lines(cbind(excu_95,excu_98,excu_102,excu_105), col = "orange", on=1, lty=2, lwd = 3)
  addLegend(legend.loc = 'topleft', legend.names = c("5% and 95% Percentile for all simulations",
                                                     "50% Percentile for all simulations",
                                                     "Product Strike price: 95%, 98%, 102%, 105%"), 
            lwd = c(2,2,3), lty = c(1,1,2), col = c("blue","black","orange")) } 






```



```{r results='hide'}
# Product 1
p1m1 <- matrix(ncol = 0, nrow = ncol(cum_return))
p1m2 <- matrix(ncol = 0, nrow = ncol(cum_return))
p1m3 <- matrix(ncol = 0, nrow = ncol(cum_return))
# Product 2
p2m1 <- matrix(ncol = 0, nrow = ncol(cum_return))
p2m2 <- matrix(ncol = 0, nrow = ncol(cum_return))
p2m3 <- matrix(ncol = 0, nrow = ncol(cum_return))
p2m4 <- matrix(ncol = 0, nrow = ncol(cum_return))
p2m5 <- matrix(ncol = 0, nrow = ncol(cum_return))

for (i in 1:ncol(cum_return)) {
  # Product 1
  p1m1[i] <- sum( cum_return[,i] <= 0.95, na.rm=TRUE)
  p1m2[i] <- sum( cum_return[,i] > 0.95 & cum_return[,i] <= 1.05, na.rm=TRUE)
  p1m3[i] <- sum( cum_return[,i] > 1.05, na.rm=TRUE)
  # Product 2
  p2m1[i] <- sum( cum_return[,i] <= 0.95, na.rm=TRUE)
  p2m2[i] <- sum( cum_return[,i] > 0.95 & cum_return[,i] <= 0.98, na.rm=TRUE)
  p2m3[i] <- sum( cum_return[,i] > 0.98 & cum_return[,i] <= 1.02, na.rm=TRUE)
  p2m4[i] <- sum( cum_return[,i] > 1.02 & cum_return[,i] <= 1.05, na.rm=TRUE)
  p2m5[i] <- sum( cum_return[,i] > 1.05, na.rm=TRUE)
}


```



```{r fig.width=12, fig.height=6, message=FALSE, warning=FALSE}
# paste0("Product 1 Total Return = " , p1m1," * 0% + ", p1m2,"* 4.4% + ", p1m3, "* 0%","+ 0.1% = ", rproduct1)
rproduct1 <- (p1m1*0 + p1m2*0.044 + p1m3*0 + 0.001)/nrow(cum_return)
data <- rproduct1
hist(data, breaks = 300, xaxt="n",xlab="",main = "",probability=TRUE,
     sub = paste0("Mean=",round(mean(data)*100,3),"%",
                  ", StdDev=",round(sd(data*100),3),"%",
                  ", Median=",round(median(data*100),3),"%",
                  ", Mode=",round(getmode(data*100),3),"%",
                  ", Skew=",round(e1071::skewness(data),3),
                  ", Kurt=",round(e1071::kurtosis(data),3),"+3",
                  ", \nMax=",round(max(data)*100,3),"%",
                  ", Min=",round(min(data)*100,3),"%",
                  ", PCTL95%=",round(quantile(data, 0.95)*100,3),"%",
                  ", PCTL5%=",round(quantile(data, 0.05)*100,3),"%")) # Histogram)
title(main = paste0("Simulated Histogram of Product 1 Return, n=",length(data)), xlab="Total Return", adj = 0)
axis(side=1, at=pretty(x=data,n=22), 
     lab=paste0(pretty(data,n=22) * 100,"%"), las=2) # x tick

abline(v = getmode(data), col = "cyan",lty = 3)
abline(v = quantile(data, 0.025), col = "Black",lty = 3)
abline(v = quantile(data, 0.975), col = "Black",lty = 3)
abline(v = median(data), col = "Green",lty = 3)
abline(v = mean(data), col = "Purple",lty = 3)
abline(v = quantile(data, c(0.25, 0.75)), col = "Orange",lty = 3)
boxplot(data, add=TRUE,horizontal=TRUE,at=-1.25,col = "lightgray",
        border="black",boxwex=3.5,outline=TRUE,xlab="n", ylab="n",axes=FALSE)



rproduct2 <- (p2m1*0 + p2m2*0.03 + p2m3*0.059 + p2m4*0.003 + p2m5*0 + 0.001)/nrow(cum_return)
data <- rproduct2
hist(data, breaks = 300, xaxt="n",xlab="",main = "",probability=TRUE,
     sub = paste0("Mean=",round(mean(data)*100,3),"%",
                  ", StdDev=",round(sd(data*100),3),"%",
                  ", Median=",round(median(data*100),3),"%",
                  ", Mode=",round(getmode(data*100),3),"%",
                  ", Skew=",round(e1071::skewness(data),3),
                  ", Kurt=",round(e1071::kurtosis(data),3),"+3",
                  ", \nMax=",round(max(data)*100,3),"%",
                  ", Min=",round(min(data)*100,3),"%",
                  ", PCTL95%=",round(quantile(data, 0.95)*100,3),"%",
                  ", PCTL5%=",round(quantile(data, 0.05)*100,3),"%")) # Histogram)
title(main = paste0("Simulated Histogram of Product 2 Return, n=",length(data)), xlab="Total Return", adj = 0)
axis(side=1, at=pretty(x=data,n=22), 
     lab=paste0(pretty(data,n=22) * 100,"%"), las=2) # x tick

abline(v = getmode(data), col = "cyan",lty = 3)
abline(v = quantile(data, 0.025), col = "Black",lty = 3)
abline(v = quantile(data, 0.975), col = "Black",lty = 3)
abline(v = median(data), col = "Green",lty = 3)
abline(v = mean(data), col = "Purple",lty = 3)
abline(v = quantile(data, c(0.25, 0.75)), col = "Orange",lty = 3)
boxplot(data, add=TRUE,horizontal=TRUE,at=-1.25,col = "lightgray",
        border="black",boxwex=3.5,outline=TRUE,xlab="n", ylab="n",axes=FALSE)
```







